### 2012-05-24 web/12.su.reg/exams/exam3.su.12.tex
Rename to avoid clash with PDF file.

\vfill
\centerline{\Large CS 2510 Exam 2 -- Summer 2012}

@@

\textit{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{4.5cm}
\begin{tabular}{|c|l@{\qquad\qquad}|r|}
\hline
\textbf{Score} &  & 30 \\ \hline
\end{tabular}
\end{minipage}

@@

%% -----------------------------------------------------------------------------
%% 
\pts{30}
\begin{problem}

Binary trees are one of the most widely used data structures in
computer science.  Here are three examples of binary trees of numbers:

\begin{verbatim}
         5        1           3
                   \         / \
                    2       4  18
                              /  \
                             9    12
                            /    /
                           7    3
\end{verbatim}

Nodes in a binary tree carry data, which in this case are numbers, and
a node has a left and right subtree.  Binary trees, like lists, may
contain \emph{any} number of elements, including 5, 8, 19, and 0.

\begin{enumerate}
\item Design a data definition for binary trees.  It must adequately
  represent any possible binary tree.

\item Give class diagrams corresponding to the data definition from
  part A.

\item Design a {\tt mirror} method that computes the mirror image of a
  binary tree.  For example, the mirror image of the above trees would
  be:

\begin{verbatim}
     5        1           3
             /           / \
            2           18  4
                       /  \
                     12    9
                       \    \
                        3    7
\end{verbatim}
\end{enumerate}

\end{problem}
\newpage
\ 
\end{document}

>>>>

\vfill
\centerline{\Large CS 2510 Exam 3 -- Summer 2012}

@@

\textit{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{4.5cm}
\begin{tabular}{|c|l@{\qquad\qquad}|r|}
\hline
\textbf{Score} &  & 45 \\ \hline
\end{tabular}
\end{minipage}

@@

%% -----------------------------------------------------------------------------
%% 
\pts{15}
\begin{problem}
We've seen multiple instances of objects representing functions, such
as predicates and comparison functions.  The general idea for
representing a function with contract {\tt A -> B} is to use an object
with an {\tt apply} method that consumes an {\tt A} and produces a
{\tt B}:

\begin{verbatim}
// Represents a function from A to B.
interface Fun<A,B> {
  // Apply this function to given argument.
  B apply(A a);
}
\end{verbatim}

Design an implementation of {\tt Fun<Posn,Double>} that calculates the
distance from the origin to the posn.  You may assume the following
data definition for {\tt Posn} (with the usual constructor):

\begin{verbatim}
// Represents a point on a Cartesian plane
class Posn {
  Integer x;
  Integer y;
}
\end{verbatim}

Hint: the distance between two points is given by
$\sqrt{(x_2-x_1)^2+(y_2-y_1)^2}$ and {\tt Math.sqrt} and {\tt
  Math.sqr} calculate what their names suggest.

\end{problem}
\newpage
\pts{15}
\begin{problem}
Assume the following definition for {\tt ListVisitor<X,R>}:

\begin{verbatim}
// Represents a computation over a list of X producing an R.
interface ListVisitor<X,R> {
  R visitEmpty();
  R visitCons(X first, List<X> rest);
}
\end{verbatim}

Design an implementation of {\tt ListVisitor<X,List<Y>>} that maps a
given function (of type {\tt Fun<X,Y>}) over a list of {\tt X} to
produce a list of {\tt Y}.

\end{problem}
\newpage

\pts{15}
\begin{problem}
Design an implementation of {\tt ListVisitor<X,X>} that produces the
first element of a non-empty list that minimizes the result of a given
{\tt Fun<X,Double>} function.  It should signal an error if the list
is empty.

For example, if given the distance function from problem 1 and a list
of {\tt Posn}s representing (4,5), (2,3), and (1,2), it should produce
the posn representing (1,2) since it closest to the origin (it
minimizes the distance function).

Hint: you should use an accumulator-based design and therefore may
need to develop two visitors.
\end{problem}
\newpage
\ 
\end{document}
